---
output: github_document
title: SATURN data overview
always_allow_html: true
---

This repository presents an overview of the different datasets that could be used for the SATURN project.

# Variables and datasets

The main variables of the SATURN project are cycling levels and road lighting. Road safety and crime are relevant. Other interesting variables are individual variables such as gender, age, income, and environmental variables such as infrastructure and spatial deprivation.

```{r echo=FALSE, message=FALSE}
library(kableExtra)

# data <- c('Traffic counts (Department for Tranport)', 'STRAVA', 'National Travel Survey (NTS)', 'Active Lives Adult Survey (ALS)', 'Transport for London (TfL) counters', 'OSM (openinfra project `oi_is_lit()` function)', 'nightlight-data', 'STATS19', 'FARS (Fatality Analysis Reporting System)', 'DATA POLICE UK', 'STRAVA', 'OSM', 'IMD')
# variable <- c('cycling levels', 'cycling levels', 'cycling levels', 'cycling levels', 'cycling levels', 'road lighting', 'road lighting', 'road safety', 'road safety', 'crime', 'individual variables (e.g. gender, age, etc.)', 'cycling infrastructure', 'spatial deprivation')
# area <- c('Great Britain', 'Global', 'Residents of England within Great Britain', 'England', 'London', 'Global', 'Glasgow and Edinburgh areas', 'Great Britain', 'US', 'England, Wales and Northern Ireland', 'Global', 'Global', 'England')
# years <- c('1993-2021', '2010-2021', '2010-2021', '2017-2021', '2013-2022', '2012-2021', '2021, 2022', '1979-2021', '1975-2020', '2013-2022', '2010-2022', '2015-2018', '2019')

# df <- data.frame(data, variable, area, years)

# colnames(df) <- c('Dataset', 'Variable', 'Geographical coverage', 'Years')
# readr::write_csv(df, "active-travel-lighting-datasets.csv")
df = readr::read_csv("active-travel-lighting-datasets.csv")
kbl(df) %>%
  kable_styling()

```

<!-- # Cycling levels -->

<!-- One of the main challenges of the SATURN project is which dataset to choose as a proxy for cycling levels. Several possibilities are being considered. The following table shows the pros and cons of each of them. -->

```{r eval=FALSE, include=FALSE}

data <- c('Traffic counts (Department for Tranport)', 'STRAVA', 'National Travel Survey (NTS)', 'Active Lives Adult Survey (ALS)', 'Transport for London (TfL) counters')
area <- c('Great Britain', 'Global', 'Residents of England within Great Britain', 'England', 'London')
years <- c('1993-2021', '2010-2021', '2010-2021', '2017-2021', '2013-2022')
pros <- c('up-to-date', 'up-to-date, gender and age', 'nationwide coverage, other individual variables', 'nationwide coverage, other individual variables', 'up-to-date')
cons <- c('not consistent, different locations/year', 'bias/representativeness', 'up to regional level', 'up to Local Authority level', 'only London')

df <- data.frame(data, area, years, pros, cons)

colnames(df) <- c('Dataset', 'Geographical coverage', 'Years', 'Pros', 'Cons')
kbl(df) %>%
  kable_styling()
```

# Relevant links

- Traffic counts: https://roadtraffic.dft.gov.uk/downloads, https://github.com/ITSLeeds/dftTrafficCounts

- STRAVA Metro data https://www.ubdc.ac.uk/data-services/data-catalogue/transport-and-mobility-data/strava-metro-data/

- National Travel Survey https://www.gov.uk/government/collections/national-travel-survey-statistics

- Active Lives Survey https://www.sportengland.org/research-and-data/data/active-lives

- TfL cycle counts https://cycling.data.tfl.gov.uk/

- Safer Active project: https://saferactive.github.io/trafficalmr/articles/report3.html,  https://saferactive.github.io/trafficalmr/articles/report4.html, https://github.com/saferactive/saferactive/blob/master/code/tests/bradford-and-beyond.md

- Lighting presence https://udsleeds.github.io/openinfra/reference/oi_is_lit.html; http://ubdc.gla.ac.uk/dataset/nightlight-data

- VIIRS link: https://developers.google.com/earth-engine/datasets/catalog/NOAA_VIIRS_DNB_MONTHLY_V1_VCMSLCFG

- Road safety: https://www.data.gov.uk/dataset/cb7ae6f0-4be6-4935-9277-47e5ce24a11f/road-safety-data, https://cran.r-project.org/web/packages/stats19/index.html, https://elipousson.github.io/crashapi/, https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars

- Crime: https://data.police.uk/data/archive/; https://github.com/njtierney/ukpolice

- Infrastructure: https://github.com/udsleeds/openinfra/issues/105, https://github.com/udsleeds/openinfra/blob/main/data-small/atf-funds.csv
